### 2025-03-13 acronyms/acronyms.tex
miles
acronyms
gps

@@

\newacronym{sbe}{SBE}{Idaho State Board of Education}
\newacronym{sde}{SDE}{Idaho State Department of Education}

@@

@@

>>>>

\newacronym{msm}{MSE}{Micron School of Materials Science and Engineering}

@@

\newacronym{sbe}{ISBE}{Idaho State Board of Education}
\newacronym{sde}{ISDE}{Idaho State Department of Education}

@@

\newacronym{gps}{GPS}{Global Positioning System}

@@

\newacronym{mls}{MILES}{Managing Idaho's Landscapes for Ecosystem Services}
